\thesistitle

### 2019-08-17 sections/results.tex
Added location table

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).

>>>>

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{chap:clonelocations}).
\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Category & Clone instances & \% \\ \midrule
Method Level & 232,532 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
Outside & 13 & 0.00\% \\ \bottomrule
\end{tabular}
\caption{Amount of clone instances with a certain location}
\label{tab:location}
\end{table}
